Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-03-29 rebuttal/ijcai21-authors-response.tex
Full VS partial profiles
Phrasing
rebuttal comments

	We thank the reviewers for their comments. We focus on factual errors and on the “questions for the authors”.

\paragraph{Review $\#$2 writes as a weakness that “the method proposed here is not compared with others”.}
We believe it is erroneous to consider the lack of comparison a weakness. The simultaneous elicitation of both the voting rule and the agents preferences is a novel setting and, as far as we know, there is no competitor from the state-of-the-art to compare with. 
We are not aware of any method that elicits the voting rule we could compare with – the work by Cailloux and Endriss [2014] does not consider PSRs. Nevertheless, the Two Phases strategy was designed to challenge our interleaving approach by comparing it with a more classical sequential method, which (when first eliciting the rule and then the agents preferences) coincides with the method of Lu and Boutilier [2011] for preferences elicitation with a fixed voting rule.
%\paragraph{Review $\#$2: “Only variants of the same methods are compared with each others”.}
%\commentOC{Isn’t this a bit arguable that Elitist is very different rather than a variant?}
The Elitist strategy has a very different approach than the Pessimistic one, to the point that it cannot be considered a variant. They are compared in a situation specifically tailored to advantage the Elitist.

@@

>>>>

	We thank the reviewers for their comments. We focus on factual errors and on the “questions for the authors”. \commentBN{Maybe: "We focus on factual errors and only on the questions reported in “questions for the authors”", or "We focus on factual errors when not better specified." and we write a Q before the questions.}

\paragraph{Review $\#$2 writes as a weakness that “the method proposed here is not compared with others”.}
We believe it is erroneous to consider the lack of comparison a weakness. The simultaneous elicitation of both the voting rule and the agents preferences is a novel setting and, as far as we know, there is no competitor from the state-of-the-art to compare with. 
We are not aware of any method that elicits the voting rule we could compare with – the work by Cailloux and Endriss [2014] does not consider PSRs. Nevertheless, the Two Phases strategy was designed to challenge our interleaving approach by comparing it with a more classical sequential method, which (when first eliciting the rule and then the agents preferences) coincides with the method of Lu and Boutilier [2011] for preferences elicitation with a fixed voting rule.
%\paragraph{Review $\#$2: “Only variants of the same methods are compared with each others”.}
%\commentOC{Isn’t this a bit arguable that Elitist is very different rather than a variant?}
The Elitist strategy has a very different approach than the Pessimistic one and does not use the regret to question the voters. It was conceived to challenge our best strategy (Pessimistic) in extreme cases tailored to favor Elitist.
\commentBN{I removed "to the point that it cannot be considered a variant", it's arguable, maybe it's better to not focus on this.}

@@

\commentBN{If we want to keep this we could summarize it as follows}
Yes, when we do not specify the name of the dataset we mean data generated following the procedure described in Sec 5. We designed several strategies in order to challenge one another and select the best strategy in the worst case (Impartial Culture). Once this was found to be Pessimistic, we tested it on real dataset.
